Total Platform Cyber Protection

### 2016-08-23 paper.tex
cleanup and adding more todos

%TODO Adam: Not sure if anon submission so just leaving like this for now
\author{
%First Author
%\affil{Arizona State University}
%Second Author
%\affil{Arizona State University}
%Third Author
%\affil{Arizona State University}
%Fourth Author
%\affil{Arizona State University}
%Fifth Author
%\affil{Arizona State University}
%Sixth Author
%\affil{Arizona State University}
%Seventh Author
%\affil{Arizona State University}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

% TODO Sai: Discuss story with yeganeh and get a nice little abstract here
\begin{abstract}
Multifrequency media access control has been well understood in
general wireless ad hoc networks, while in wireless sensor networks,
researchers still focus on single frequency solutions. In wireless
sensor networks, each device is typically equipped with a single
radio transceiver and applications adopt much smaller packet sizes
compared to those in general wireless ad hoc networks. Hence, the
multifrequency MAC protocols proposed for general wireless ad hoc
networks are not suitable for wireless sensor network applications,
which we further demonstrate through our simulation experiments. In
this article, we propose MMSN, which takes advantage of
multifrequency availability while, at the same time, takes into
consideration the restrictions of wireless sensor networks. Through
extensive experiments, MMSN exhibits the prominent ability to utilize
parallel transmissions among neighboring nodes. When multiple physical
frequencies are available, it also achieves increased energy
efficiency, demonstrating the ability to work against radio
interference and the tolerance to a wide range of measured time
synchronization errors.
\end{abstract}

@@

%TODO Sai: Add keywords here
\keywords{}

\acmformat{, 2016. Total Platform Cyber Protection.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

@@

Much of the prior research focuses on just looking at memory
corruption bugs, but we need to look at how the same sort of advanced
protections can be applied to other classes of bugs, i.e., what is
next? This includes: input validation, logic problems, leaking
secrets, performance degradation, denial-of-service, command (e.g.,
SQL) injection, and concurrency attacks.

@@

\begin{enumerate}
	\item Dealing with bloat and reducing the attack surface
	\item Instrumentation is easier at this layer, but faster ways to observe execution are needed
	\item Controlling easily misued middleware APIs (confused deputy)
\end{enumerate}

@@

In this article, we develop the first multifrequency MAC protocol for
WSN applications in which each device adopts a
single radio transceiver. The different MAC design requirements for
WSNs and general wireless ad-hoc networks are
compared, and a complete WSN multifrequency MAC design (MMSN) is
put forth. During the MMSN design, we analyze and evaluate different
choices for frequency assignments and also discuss the nonuniform
back-off algorithms for the slotted media access design.

% Appendix
\appendix
\section*{APPENDIX}
\setcounter{section}{1}
In this appendix, we measure
the channel switching time of Micaz [CROSSBOW] sensor devices.
In our experiments, one mote alternatingly switches between Channels
11 and 12. Every time after the node switches to a channel, it sends
out a packet immediately and then changes to a new channel as soon
as the transmission is finished. We measure the
number of packets the test mote can send in 10 seconds, denoted as
$N_{1}$. In contrast, we also measure the same value of the test
mote without switching channels, denoted as $N_{2}$. We calculate
the channel-switching time $s$ as
\begin{eqnarray}%
s=\frac{10}{N_{1}}-\frac{10}{N_{2}}. \nonumber
\end{eqnarray}%
By repeating the experiments 100 times, we get the average
channel-switching time of Micaz motes: 24.3$\mu$s.

\appendixhead{ZHOU}

% Acknowledgments
\begin{acks}

\end{acks}

>>>>

% TODO Adam: Not sure if anon submission so just leaving like this for now
\author{
%First Author
%\affil{Arizona State University}
%Second Author
%\affil{Arizona State University}
%Third Author
%\affil{Arizona State University}
%Fourth Author
%\affil{Arizona State University}
%Fifth Author
%\affil{Arizona State University}
%Sixth Author
%\affil{Arizona State University}
%Seventh Author
%\affil{Arizona State University}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

% TODO Sai: Discuss story with yeganeh and get a nice little abstract here
\begin{abstract}
Abstract goes here
\end{abstract}

@@

% TODO Sai: Add keywords here
\keywords{}

\acmformat{\emph{Data needed here}, 2016. Total Platform Cyber Protection.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

% TODO Sai: make `Suggested Focus Areas` and `Focus Areas` consistent 
\subsection{Suggested Focus Areas}

@@

\subsection{Focus Areas}
% TODO Sai: Definitely needs a smoother transition from above, why are we saying research here 
%%is inadequate and looks at only mem-corruption bugs? what is the basis?
Much of the prior research focuses on just looking at memory
corruption bugs, but we need to look at how the same sort of advanced
protections can be applied to other classes of bugs, i.e., what is
next? This includes: input validation, logic problems, leaking
secrets, performance degradation, denial-of-service, command (e.g.,
SQL) injection, and concurrency attacks.

@@

% TODO Sai: WHAT is this?
%\subsection{Focus Areas}
%
%\begin{enumerate}
%	\item Dealing with bloat and reducing the attack surface
%	\item Instrumentation is easier at this layer, but faster ways to observe execution are needed
%	\item Controlling easily misused middleware APIs (confused deputy)
%\end{enumerate}

@@

%% Appendix
%\appendix
%\section*{APPENDIX}
%\setcounter{section}{1}
%\appendixhead{}
%
%% Acknowledgments
%\begin{acks}
%
%\end{acks}
